---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![Travis-CI Build Status](https://travis-ci.org/kota7/withcon.svg?branch=master)](https://travis-ci.org/kota7/withcon)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/kota7/withcon?branch=master&svg=true)](https://ci.appveyor.com/project/kota7/withcon)

# withcon


`withcon` is an R package that provides functionality 
similar to the `with` clause in Python;
It automatically closes connections after a series of operations and 
also when an exception occurs during the operations.

Currently the functionality is provided for `connection` objects 
(created *e.g.* by `file` and `gzfile`) and 
`DBIConnection` objects (created by `DBI::dbConnect`).


## Example

```{r example}
library(withcon)
library(DBI)
res <- withCon(conn = dbConnect(RSQLite::SQLite(), ':memory:'), do = {
  dbWriteTable(conn, 'tbl', mtcars)
  dbReadTable(conn, 'tbl')
})
head(res)
```
